### 2010-03-17 papers/icfp-2010-desc/paper_idesc.tex
IDesc@ICFP: typos.

To get a clue of a solution, let us look back at $\Fin$. We note that
the equation is introduced because we are \emph{storing} the index of
the inductive family, through $m$. Hence the constraint. However,
\emph{inductive families need not store their
  indices}~\cite{brady:index-inductive-families}. Applying the
\emph{forcing} optimisation to our definition of $\Fin$ gives the
following, equivalent definition:

\note{ I'm not familiar with this, I need to get into the paper. }

@@

The resulting data-type is called $\HExprFreeD$. By a simple unfolding
of definition, we note that $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}$
corresponds to the closed expression, $\HExprD$. Similarly,
$$\FreeIMonad{\HExprFreeD}{\Ty}{(\LAM{ty} \Val{ty} + \Var{ty})}$$
corresponds to expressions with variables, $\HExprVarD$.

>>>>

To get a clue of a solution, let us look back at $\Fin$. We note that
the equation is introduced because we are \emph{storing} the index of
the inductive family, through $m$. Hence the constraint. However,
\emph{inductive families need not store their
  indices}~\cite{brady:index-inductive-families}\note{ I'm not
  familiar with this, I need to get into the paper. }. Applying the
\emph{forcing} optimisation to our definition of $\Fin$ gives the
following, equivalent definition:

@@

The resulting data-type is called $\HExprFreeD$. By a simple unfolding
of definition, we note that $\FreeIMonad{\HExprFreeD}{\Ty}{\Val{}}$
corresponds to the closed expression, $\HExprD$. Similarly,
$$\FreeIMonad{\HExprFreeD}{\Ty}{(\LAM{ty} \Val{ty} + \Var{dom}{ty})}$$
corresponds to expressions with variables, $\HExprVarD$.
